\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-19 paper/paper.tex
Added some plots and small paper edits.

For all of the models we consider, the parameters for the infant mortality failure mode are held in common across drive brand models. We found that there was insufficient information in the data to model these parameters hierarchically.  Moreover, assuming a common distribution for infant mortality allows for straightforward interpretation of the quantities like $\frac{\pi_{d}}{\pi_{d'}}$.

@@

\subsection{Model Comparisons}
First look at the overlaid posterior credible bands. \\

@@

\subsection{Brand Comparisons}
Ideas for plots: A graph comparing the pi's for all drive models.

I think a graph looking at the B10 using the full model could be good, too.  Something like the graph below.  Perhaps we could sort drive model based on sample size?

This should probably be truncated at something like eight years, since the right tails seem unlikely. Sort by left endpoint?

@@

>>>>

For all of the models we consider, the parameters for the infant mortality failure mode are held in common across drive brand models. We found that there was insufficient information in the data to model these parameters hierarchically.  Moreover, assuming a common distribution for infant mortality provides a meaningful interpretation and comparison of the various ${\pi_{d}$, the probability of infant mortality for drive model $d$.

@@

\subsection{Model Comparisons}
First look at the overlaid posterior credible bands.  Perhaps pick 4 different drive models and present a plot like the figure below.  Bands are for full model, and the solid line is the full model fit. \\

\begin{figure}[H]
    \centering
   \includegraphics[width=5.0in]{fig/mod40_bands.pdf}
		\caption{Drive Model 40 \label{fig:first}} 
\end{figure}

@@

\subsection{Brand Comparisons}

@@

Am wondering if we should truncate this graph at a reasonable value, perhaps .3 or .2?

\begin{figure}[H]
    \centering
   \includegraphics[width=5.0in]{fig/pi_bymod.pdf}
		\caption{$\pi$ for All Drive Models \label{fig:first}} 
\end{figure}
